Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks

### 2016-10-24 PCE_paper/manuscript_gmes.Rmd
fixed mistakes from proofs

\
The distribution of resources required for *A*~n~, including leaf nitrogen (N) and supply of water, are also partially defined by canopy light gradients. As *A*~n~ has a saturating response with light and maximum rates depend, in part, on N-rich photosynthetic machinery, it has been argued that leaf N should be proportional to PPFD along the canopy light gradient to maximize canopy C gain at a given total canopy N [@field1983allocating; @field1986photosynthesis; @peltoniemi2012co; @buckley2013does]. Changes in chlorophyll per unit N, chlorophyll a:b ratios, electron transport capacity per unit chlorophyll and ratios of electron transport capacity to Rubisco activity can also occur in response to changes in irradiance of the growth environment [@evans2001photosynthetic]. Sun leaves frequently experience greater water limitations in the upper canopy, despite effective vascular systems that accommodate high radiation loads and transpiration [@sellin2008effects; @niinemets2012optimization]. Optimal photosynthetic N investment in the upper canopy will be ineffective in enhancing *A*~n~ if water supply is insufficient [@niinemets2012optimization; @peltoniemi2012co]; thus leaf-specific  hydraulic conductance (*K*~L~) should also be higher in the upper canopy to supply sunlit leaves with sufficient water [@burgess2006hydraulic;@sellin2007effects ;@sellin2008effects;@hubbard2001stomatal].

@@

\
We found that *A*~n~ and *g*~m~ scaled positively across leaf types (Fig. 3b) and, unexpectedly, increased in shade leaves when light intensity was increased to values similar in sun leaves. Comparable LMA within the canopy likely allowed for this up-regulation of *g*~m~ , which played a critical role in the photosynthetic response of shade leaves to sunflecks. Components of LMA, such as palisade thickness and cell surface exposed to intercellular air space, set an upper limit for *g*~m~, but considerable variation in *g*~m~ can exist for a given LMA [@flexas2008mesophyll; @milla2016leaf]. Possible mechanisms for the rapid (~25 min) up-regulation of *g*~m~ to light intensity include regulation of aquaporins, which can facilitate increases in the CO~2~ permeability of the cell membranes [@hanba2004overexpression; @heinen2009role; @li2014plant] or movement of chloroplasts to facilitate CO~2~ diffusion [@tholen2008]. It has also been proposed that *g*~m~ and *K*~L~ should be coordinated, as optimizing hydraulic supply allows both *g*~s~ and *g*~m~ to enhance *A*~n~ [@flexas2013leaf]. Here, higher *K*~l~ in shade leaves under high light lends support to the potential coordination *K*~l~ and *g*~m~ and also to the association of higher *A*~n~ with higher *K*~l~ when light becomes saturating, as reported by @franks2006higher.

\
If shade leaves "lie in wait" for sunflecks, then perhaps we should consider an alternate leaf economic strategy to maximize C gain, beyond conventional trade-offs associated with canopy resource distribution. This is because the role of *g*~s~ in regulating photosynthetic induction impacts the capacity of a leaf to utilize sunflecks [@way2012sunflecks]. If the valuation of sunflecks as a C resource is large enough, then costs of sub-optimal stomatal behaviour could be offset over the leaf lifespan or across the entire canopy when considering both sun and shade leaf types [@vicomanz2011]. For example, the potential C gain in leaves where sunflecks constitute a large proportion of total daily PFFD may be large enough to accommodate the cost of increased water use in the shade. However, accounting for the heterogeneous nature of light within a canopy remains a current challenge for empirical and modelling studies. Thus, models which predict leaf photosynthesis from N distribution within a canopy will be incomplete unless inclusion of canopy light extinction and the integration of sunflecks on shade leaves are included [@de1997simple].

>>>>

\
The distribution of resources required for *A*~n~, including leaf nitrogen (N) and supply of water, is also partially defined by canopy light gradients. As *A*~n~ has a saturating response with light and maximum rates depend, in part, on N-rich photosynthetic machinery, it has been argued that leaf N should be proportional to PPFD along the canopy light gradient to maximize canopy C gain at a given total canopy N [@field1983allocating; @field1986photosynthesis; @peltoniemi2012co; @buckley2013does]. Changes in chlorophyll per unit N, chlorophyll a:b ratios, electron transport capacity per unit chlorophyll and ratios of electron transport capacity to Rubisco activity can also occur in response to changes in irradiance of the growth environment [@evans2001photosynthetic]. Sun leaves frequently experience greater water limitations in the upper canopy, despite effective vascular systems that accommodate high radiation loads and transpiration [@sellin2008effects; @niinemets2012optimization]. Optimal photosynthetic N investment in the upper canopy will be ineffective in enhancing *A*~n~ if water supply is insufficient [@niinemets2012optimization; @peltoniemi2012co]; thus leaf-specific  hydraulic conductance (*K*~L~) should also be higher in the upper canopy to supply sunlit leaves with sufficient water [@burgess2006hydraulic;@sellin2007effects ;@sellin2008effects;@hubbard2001stomatal].

@@

\
We found that *A*~n~ and *g*~m~ scaled positively across leaf types (Fig. 3b) and, unexpectedly, increased in shade leaves when light intensity was increased to values similar in sun leaves. Comparable LMA within the canopy likely allowed for this up-regulation of *g*~m~ , which played a critical role in the photosynthetic response of shade leaves to sunflecks. Components of LMA, such as palisade thickness and cell surface exposed to intercellular air space, set an upper limit for *g*~m~, but considerable variation in *g*~m~ can exist for a given LMA [@flexas2008mesophyll; @milla2016leaf]. Possible mechanisms for the rapid (~25 min) up-regulation of *g*~m~ to light intensity include regulation of aquaporins, which can facilitate increases in the CO~2~ permeability of the cell membranes [@hanba2004overexpression; @heinen2009role; @li2014plant] or movement of chloroplasts to facilitate CO~2~ diffusion [@tholen2008]. It has also been proposed that *g*~m~ and *K*~L~ should be coordinated, as optimizing hydraulic supply allows both *g*~s~ and *g*~m~ to enhance *A*~n~ [@flexas2013leaf]. Here, higher *K*~L~ in shade leaves under high light lends support to the potential coordination *K*~L~ and *g*~m~ and also to the association of higher *A*~n~ with higher *K*~L~ when light becomes saturating, as reported by @franks2006higher.

\
If shade leaves "lie in wait" for sunflecks, then perhaps we should consider an alternate leaf economic strategy to maximize C gain, beyond conventional trade-offs associated with canopy resource distribution. This is because the role of *g*~s~ in regulating photosynthetic induction impacts the capacity of a leaf to utilize sunflecks [@way2012sunflecks]. If the valuation of sunflecks as a C resource is large enough, then costs of sub-optimal stomatal behaviour could be offset over the leaf lifespan or across the entire canopy when considering both sun and shade leaf types [@vicomanz2011]. For example, the potential C gain in leaves where sunflecks constitute a large proportion of total daily PPFD may be large enough to accommodate the cost of increased water use in the shade. However, accounting for the heterogeneous nature of light within a canopy remains a current challenge for empirical and modelling studies. Thus, models which predict leaf photosynthesis from N distribution within a canopy will be incomplete unless inclusion of canopy light extinction and the integration of sunflecks on shade leaves are included [@de1997simple].
